%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software/Hardware Team Lead} % Job title
    {International Cybernetics} % Organization
    {Clearwater, FL} % Location
    {Oct 2022 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Lead a team of 4 engineers in the maintenance and development of a data acquisition system}
        \item {Developed modern C++ code for a Linux backend data collector computer, and a Windows GUI}
        \item {Integrated new sensors into a hardware application in charge of collecting data from multiple communication interfaces.}
        \item {Implemented industry-specific algorithms in accordance with industry standards}
        \item {\it{Promotions:} Hardware/Software Team Lead (2023)}
      \item {\it{Technologies:} C++, C\#, docker, CircleCI, VS2022, I2C, UART, Raspberry Pi Pico}
    \end{cvitems}
    }
  \cventry
    {Senior Advanced Software Engineer} % Job title
    {Honeywell Aerospace International} % Organization
    {Clearwater, FL} % Location
    {May 2015 - Oct 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Maintain and enhance a C++ based testing framework.}
				\item {This framework controls several hardware interfaces, such as: Power Supplies, DIO modules, relays, oscilloscopes, and various National Instruments analysis cards.}
        \item {Implemented graphical user interface to display data from various Inertial Navigation Systems.}
				\item {Improved automated test scripting standards, test review checklists, and test execution procedures, significantly reducing review and execution time.}
        \item {\it{Promotions:} Software Engineer II (2017), Senior Software Engineer (2019), Senior Advanced Software Engineer (2021)}
        \item {\it{Technologies:} C++, C\#, Visual Studio, Python, MIL1553, RS232, NI LabWindows/CVI}
        \item {\it {Awards:} Honeywell Aerospace 2017 Outstanding Engineers.}
      \end{cvitems}
    }

	\cventry
		{Electrical Test Intern} % Affiliation/role
		{BlackBerry} % Organization/group
		{Ft. Lauderdale, FL} % Location
		{Fall - 2014} % Date(s)
		{
			\begin{cvitems} % Description(s) of experience/contributions/knowledge
			\item {Member of the handheld hardware development team responsible for the design, integration, and verification of the baseband and digital subsystems for a mobile computing design.}
			\item {Directly responsible for testing all communication interfaces.}
			\end{cvitems}
		}
%---------------------------------------------------------
\end{cventries}
