%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Summary}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvparagraph}

%---------------------------------------------------------
% Add bullets to this list
\begin{itemize}
\begin{item}
Highly experienced software developer with over 8 years of experience in developing software. Graduated as an Electrical Engineer but quickly developed a passion for software development. Started career at Honeywell, where I developed test software for the equipment manufactured there. Pursued a Masters in Software Development to further enhance my skills.
\end{item}
\begin{item}
During my time at Honeywell, I gained expertise in developing test software that interfaced with various NI cards, controlled power supplies, relays, oscilloscopes, and digital multimeters.
\end{item}
\begin{item}
Now, at ICC, I work on integrating new sensors into a data acquisition hardware platform. I have extensive experience in hardware-software integration, working with oscilloscopes, digital multimeters (DMMs), digital signal analyzers, and various communication interfaces. Additionally, I developed code for a cross-platform backend application in modern C++ that runs on Linux and Windows, utilizing CMake and Visual Studio for build systems.
\end{item}
\begin{item}
I am passionate about software development, my main language for development is C++, although I also have experience in C, Python, C\#, and many more languages. I possess a strong background in Linux CLI applications and am dedicated to continuously expanding my knowledge and skills in the field of software development.
\end{item}
\end{itemize}

\end{cvparagraph}
